---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ussie

<!-- badges: start -->
[![R-CMD-check](https://github.com/supermdat/ussie/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/supermdat/ussie/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

This is a demo package for the "Building Tidy Tools" workshop at 
rstudio::conf(2022L). It allows you to work with European soccer league data 
supplied by the engsoccerdata package (Curley 2016).

## Installation

You can install the development version of ussie from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("supermdat/ussie")
```

## Example

This is a basic example which shows you how to obtain data from the Italian 
soccer league:

```{r example}
library(ussie)

italy <- uss_make_matches(data_engsoc = engsoccerdata::italy,
                          country = "Italy"
                          )

dplyr::glimpse(italy)
```


You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.


